\Large\textbf{Decentralized Data Marketplace to Enable Trusted Machine Economy}

### 2019-09-08 paper.tex

\section{\normalsize\textbf{Conclusion}}

>>>>

\section{\normalsize\textbf{Future Work}}
%Data Auction
The data auction process is a data trading mechanism and an economically-driven scheme that establishes corresponding prices of data products through bidding process between consumers and providers. While there has been many auction models\cite{BigPicDataMarket} in several areas, only a few of research focus on third-party auction platform. Our proposed decentralized data marketplace protects the privacy of participants which reveals the minimum information for validation and reduces the suspicion of trust to centralized parties or auctioneers. However, the auction process between multiple participants and analyzing potential threats are still critical issues that need to be resolved.
